Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-04-25 tex/scam/experiments.tex
major paper revisions

\section{Experiments}
\label{sec:thesims}
%\subsection{Simulations}
We first illustrate our methods using a simulation of the model
\begin{equation}\nonumber
         Y_i = \x_{iS}^{\top}\Q\x_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
\end{equation}
Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0}, \Sigma)$, 
$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
represents the relevant variable set, and 
$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
Note that if $\Q$ is diagonal, then the true function is convex
additive; 
otherwise the true function is convex but not additive.
For all simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.

@@

In the second simulation, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
$n=100,200,\ldots,1000$. We use independent design by seting $\Sigma = \textrm{I}_p$. We again run the AC/DC optimization on $100$
independently generated data sets and plot the probability of recovery
in Figure \ref{Support}(c). The results demonstrate that AC/DC performs
consistent variable selection even if the true function is not additive (but
still convex).

@@

We first use all $n=506$ samples (with standardization) in the AC/DC algorithm,
using a set of candidate regularization parameters $\{\lambda^{(t)}\}$
ranging from $\lambda^{(1)} = 0$ (no regularization) to $2$. For each $\lambda^{(t)}$
we obtain a function value matrix $\bds{h}^{(t)}$ with $p=13$
columns. The non-zero columns in this matrix indicate the variables selected
using $\lambda^{(t)}$.  We plot $\|\bds{h}^{(t)}\|_{\infty}$ and
the column-wise mean of $\bds{h}^{(t)}$ versus the normalized norm
$\frac{\|\bds{h}^{(t)}\|_{\infty,1}}{\|\bds{h}^{(1)}\|_{\infty,1}}$
in Figures \ref{Boston}(a) and \ref{Boston}(b).  For comparison, we
plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
From the figures we observe that the first three variables selected by
AC/DC and LASSO are the same: \tts{LSTAT}, \tts{RM} and \tts{PTRATIO},
consistent with previous findings~\citep{SpAM:07}.  The fourth
variable selected by AC/DC is \tts{INDUS} (with $\lambda^{(t)}=0.7$).
We then refit AC/DC with only these four variables without
regularization, and plot the estimated additive functions in Figure
\ref{Boston}(e). When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave if it is non-zero in the DC stage. As can be seen, these functions contain clear
nonlinear effects which cannot be captured by LASSO. The shapes of
these functions, including the concave shape of the \tts{PTRATIO} function, are in agreement with those obtained by
SpAM~\citep{SpAM:07}.

Next, in order to quantitatively study the predictive performance, we
run 3 times 5-fold cross validation, following the same procedure
described above---training, variable selection and refitting.  A plot
of the mean and standard deviation of the predictive mean squared
error (MSE) is shown in Figure \ref{Boston}(d). Since for AC/DC the same
regularization level $\lambda^{(t)}$ may lead to a slightly different number of selected
variables in different folds and runs, the values on the $x$-axis
for AC/DC are not necessarily integers. The figure clearly shows that AC/DC has a 
lower predictive MSE than LASSO.  We also compared the performance of
AC/DC with that of Additive Forward Regression (AFR) presented
in~\cite{Xi:09}, and found that they are similar.  The main advantages
of AC/DC compared with AFR and SpAM are that there are no smoothing
parameters required, and the optimization is formulated
as a convex program, guaranteeing a global optimum.

@@

\begin{center}
\begin{tabular}{cc}
%\hskip-10pt
  \includegraphics[width=.38\textwidth]{figs/acdc_path} &
%\hskip-25pt
  \includegraphics[width=.38\textwidth]{figs/lasso_path} 
\\
%\hskip-10pt 
AC/DC $\|f_k\|_\infty$ paths & 
%\hskip-25pt
LASSO $|\beta_k|$ paths \\
%\end{tabular}
%\begin{tabular}{cc}
  \includegraphics[width=.38\textwidth]{figs/MSEacdc} &
%\hskip 5pt
  \includegraphics[width=.45\textwidth]{figs/acdc_functs}
\\
predictive MSE & estimated functions from AC/DC
\end{tabular}
\end{center}
\caption{Results on Boston housing data, showing regularization paths,
 MSE and fitted functions.}\label{Boston}
\end{figure*}

>>>>

\section{Experiments}
\label{sec:thesims}
%\subsection{Simulations}
We first illustrate our methods using a simulation of the model
\begin{equation}\nonumber
         Y_i = \x_{iS}^{\top}\Q\x_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
\end{equation}
Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0}, \Sigma)$, 
$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
represents the set of relevant variables, and 
$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
Note that if $\Q$ is diagonal, then the true function is convex
additive; 
otherwise the true function is convex but not additive.
For all simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.

@@

In the second simulation, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
$n=100,200,\ldots,1000$. We use independent design by setting $\Sigma = \textrm{I}_p$. We again run the AC/DC optimization on $100$
independently generated data sets and plot the probability of recovery
in Figure \ref{Support}(c). The results demonstrate that AC/DC performs
consistent variable selection even if the true function is not additive (but
still convex).

@@

We first use all $n=506$ samples (with standardization) in the AC/DC algorithm,
using a set of candidate regularization parameters $\{\lambda^{(t)}\}$
ranging from $\lambda^{(1)} = 0$ (no regularization) to $2$. For each $\lambda^{(t)}$
we obtain a function value matrix $\bds{f}^{(t)}$ with $p=13$
columns and $n=506$ rows. The non-zero columns in this matrix indicate the variables selected using $\lambda^{(t)}$.

In Figure~\ref{Boston}(a), we plot on the y-axis the norm $\|\bds{f}^{(t)}_j\|_{\infty}$ of every column $j$ against the regularization strength $\lambda^{(t)}$. Instead of plotting the value of $\lambda^{(t)}$ on the x-axis however, we plot the total norm at $\lambda^{(t)}$ normalized against the total norm at $\lambda^{(1)}$: $\frac{\sum_j \|\bds{f}^{(t)}_j\|_{\infty}}{\sum_j \|\bds{f}^{(1)}\|_{\infty}}$. Thus, as x-axis moves from 0 to 1, the regularization goes from strong to weak. For comparison, we
plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(b).
From the figures we observe that the first three variables selected by
AC/DC and LASSO are the same: \tts{LSTAT}, \tts{RM} and \tts{PTRATIO},
consistent with previous findings~\citep{SpAM:07}.  The fourth
variable selected by AC/DC is \tts{INDUS} (with $\lambda^{(t)}=0.7$).
We then refit AC/DC with only these four variables without
regularization, and plot the estimated additive functions in Figure
\ref{Boston}(d). When refitting, we constrain a component to be convex if it is non-zero in the AC stage and concave if it is non-zero in the DC stage. As can be seen, these functions contain clear
nonlinear effects which cannot be captured by LASSO. The shapes of
these functions, including the concave shape of the \tts{PTRATIO} function, are in agreement with those obtained by
SpAM~\citep{SpAM:07}.

Next, in order to quantitatively study the predictive performance, we
run 3 times 5-fold cross validation, following the same procedure
described above---training, variable selection and refitting.  A plot
of the mean and standard deviation of the predictive mean squared
error (MSE) is shown in Figure \ref{Boston}(c). Since for AC/DC the same
regularization level $\lambda^{(t)}$ may lead to a slightly different number of selected
variables in different folds and runs, the values on the $x$-axis
for AC/DC are not necessarily integers. The figure clearly shows that AC/DC has a 
lower predictive MSE than LASSO.  We also compared the performance of
AC/DC with that of Additive Forward Regression (AFR) presented
in~\cite{Xi:09}, and found that they are similar.  The main advantages
of AC/DC compared with AFR and SpAM are that there are no smoothing
parameters required, and the optimization is formulated
as a convex program, guaranteeing a global optimum.

@@

\begin{center}
\begin{tabular}{cc}
%\hskip-10pt
  \includegraphics[width=.38\textwidth]{figs/acdc_path}  &
%\hskip-25pt
  \includegraphics[width=.38\textwidth]{figs/lasso_path} 
\\
%\hskip-10pt 
(a) AC/DC $\|f_k\|_\infty$ paths & 
%\hskip-25pt
(b) LASSO $|\beta_k|$ paths \\
%\end{tabular}
%\begin{tabular}{cc}
  \includegraphics[width=.38\textwidth]{figs/MSEacdc} &
%\hskip 5pt
  \includegraphics[width=.45\textwidth]{figs/acdc_functs}
\\
(c) predictive MSE & (d) estimated functions from AC/DC
\end{tabular}
\end{center}
\caption{Results on Boston housing data, showing regularization paths,
 MSE and fitted functions.} \label{Boston}
\end{figure*}

### 2015-04-25 tex/scam/sparsistency.tex
major paper revisions

We divide our analysis into two parts. We first establish a sufficient
deterministic condition for consistency of the sparsity pattern
screening procedure.  We then consider the stochastic setting and argue that the 
deterministic conditions hold with high probability. Note that in all of our results 
and analysis, we let $c,
C$ represent absolute constants; the actual values of $c,C$ may change from line to line. We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$. Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis. We will also assume in this section that the true regression function $f_0$ has mean-zero and therefore, we will omit the intercept term $\hat{mu}$ from our estimation procedure.

@@

\begin{definition}
\label{def:restricted_regression}
We define the \emph{restricted regression} problem 
\[
\min_{d_k} \frac{1}{n} \Big\| Y - \sum_{k \in S} \bar{\Delta}_k d_k \Big\|_2^2 + 
   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{k,1}, \ldots, d_{k,n-1} \geq 0
\]
where we restrict the indices $k$ in
optimization \eqref{opt:alternate_opt} to lie in some set $S$ which contains the true
relevant variables.
\end{definition}

@@

Let $\pi_k(i)$ be a reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry. Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere. Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.

Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > \mathsf{range}_k| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$. Suppose also that for all $k \in S^c$, $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions
supported on $[-1,1]$, 
and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
   f_k \in \mathcal{C}^1 \} $.  
Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
minimizer in $\mathcal{C}_1^p$, 
\begin{equation}
f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
\big)^2.
\end{equation}
$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-1, 1]$ and define
\begin{equation}
g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
- g_k(X_k) \big)^2.
\end{equation}
The $\hat{g}_k$'s are unique minimizers as well. We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$ and thus $s \geq s_0$. In some cases, such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent. 
\item[A2:] $f_0$ is convex and twice-differentiable. $\E f_0(X) = 0$.
\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
\item[A5:] The density $p(\mathbf{x})$ is bounded away from 0 and satisfies the boundary flatness condition. (Definition~\ref{defn:boundary-point})
\end{packed_enum}
By assumption A1, $f^*_k$ must be zero for $k\notin S$.
We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
\begin{align}
\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\} \label{eqn:signal_level_defn} \\
\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\} \nonumber
\end{align}
$\alpha_+$ is a lower bound on the excess risk incurred by any additive convex function whose support is strictly smaller than $f^*$; $\alpha_+ > 0$ since $f^*$ is the unique risk minimizer. Likewise, $\alpha_-$ lower bounds the excess risk of any decoupled concave fit of the residual $f_0 - f^*$ that is strictly more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$; $\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well. These quantities play the role of the absolute value of the smallest nonzero coefficient in the true linear model in lasso theory.  Intuitively, if
$\alpha_{+}$ is small, then it is easier to make a false omission in the
additive convex stage of the procedure. If $\alpha_{-}$ is small, then
it is easier to make a false omission in the decoupled concave stage
of the procedure.

\begin{remark}
  We make strong assumptions on the covariates in A1 in order to make
  weak assumptions on the true regression function $f_0$ in
  A2. In particular, we do not assume that $f_0$ is additive. In
  important direction for future work is to weaken assumption A1.
  Our simulation experiments indicate that the procedure can be
  effective even when the relevant and irrelevant variables are correlated.
  %Strong assumptions on the covariates are not uncommon in nonparametric
  %variable selection analysis~\cite{lafferty2008rodeo}. 
  %[TODO: refer to correlated design experiment].
\end{remark}

@@

\end{corollary}
The above corollary implies that consistent variable selection is
achievable with an exponential scaling of the ambient dimension
scaling, $p = O(\exp(n^c))$ for some $0<c<1$, just as in parametric models.
The cost of nonparametric modeling through shape constraints is
reflected in the scaling with respect to the number of relevant
variables, which can scale as $s = o(n^{4/25})$.

@@

%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "paper.tex" ***
%%% End: ***

>>>>

We divide our analysis into two parts. We first establish a sufficient
deterministic condition for consistency of the sparsity pattern
screening procedure.  We then consider the stochastic setting and argue that the 
deterministic conditions hold with high probability. Note that in all of our results 
and analysis, we let $c,
C$ represent absolute constants; the actual values of $c,C$ may change from line to line. We derived two equivalent optimizations for AC/DC: \eqref{np} outputs $\hat{f}_k, \hat{g}_k$ and \eqref{opt:alternate_opt} outputs the second derivatives $\hat{d}_k$. Their equivalence is established in Proposition~\ref{prop:alt_opt_form} and we use both $\hat{d}_k$ and $\hat{f}_k$ in our analysis. We will also assume in this section that the true regression function $f_0$ has mean-zero and therefore, we will omit the intercept term $\hat{\mu}$ from our estimation procedure.

@@

\begin{definition}
\label{def:restricted_regression}
We define the \emph{restricted regression} problem 
\[
\min_{d_k} \frac{1}{n} \Big\| Y - \sum_{k \in S} \bar{\Delta}_k d_k \Big\|_2^2 + 
   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{\pi_k(2)k}, \ldots, d_{\pi_k(n-1)k} \geq 0
\]
where we restrict the indices $k$ in
optimization \eqref{opt:alternate_opt} to lie in some set $S$ which contains the true
relevant variables.
\end{definition}

@@

Let $\pi_k(i)$ be a reordering of $X_k$ in ascending order so that $X_{\pi_k(n)k}$ is the largest entry. Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere. Define $\mathsf{range}_k = X_{\pi_k(n)k} - X_{\pi_k(1)k}$.

Suppose for all $k\in S^c$, for all $i=1,\ldots,n$, $\lambda_n > \mathsf{range}_k| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$. Suppose also that for all $k \in S^c$, $\max_{i=1,...,n-1} \frac{X_{\pi_k(i+1)k} - X_{\pi_k(i)k}}{\mathsf{range}_k} \leq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions
supported on $[-1,1]$, 
and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
   f_k \in \mathcal{C}^1 \} $.  
Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
minimizer in $\mathcal{C}_1^p$, 
\begin{equation}
f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f(X)
\big)^2.
\end{equation}
$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-1, 1]$ and define
\begin{equation}
g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
- g_k(X_k) \big)^2.
\end{equation}
The $\hat{g}_k$'s are unique minimizers as well. We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$ and thus $s \geq s_0$. In some cases, such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent. 
\item[A2:] $f_0$ is convex and twice-differentiable. $\E f_0(X) = 0$.
\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
\item[A5:] The density $p(\mathbf{x})$ is bounded away from 0 and satisfies the boundary flatness condition. (Definition~\ref{defn:boundary-point})
\end{packed_enum}
By assumption A1, $f^*_k$ must be zero for $k\notin S$.
We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
\begin{align}
\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\} \label{eqn:signal_level_defn} \\
\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\} \nonumber
\end{align}
$\alpha_+$ is a lower bound on the excess risk incurred by any additive convex function whose support is strictly smaller than $f^*$; $\alpha_+ > 0$ since $f^*$ is the unique risk minimizer. Likewise, $\alpha_-$ lower bounds the excess risk of any decoupled concave fit of the residual $f_0 - f^*$ that is strictly more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$; $\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well. These quantities play the role of the absolute value of the smallest nonzero coefficient in the true linear model in lasso theory.  Intuitively, if
$\alpha_{+}$ is small, then it is easier to make a false omission in the
additive convex stage of the procedure. If $\alpha_{-}$ is small, then
it is easier to make a false omission in the decoupled concave stage
of the procedure.

\begin{remark}
  We make strong assumptions on the covariates in A1 in order to make
  weak assumptions on the true regression function $f_0$ in
  A2. In particular, we do not assume that $f_0$ is additive. An
  important direction for future work is to weaken assumption A1.
  Our simulation experiments indicate that the procedure can be
  effective even when the relevant and irrelevant variables are correlated.
  %Strong assumptions on the covariates are not uncommon in nonparametric
  %variable selection analysis~\cite{lafferty2008rodeo}. 
  %[TODO: refer to correlated design experiment].
\end{remark}

@@

\end{corollary}
The above corollary implies that consistent variable selection is
achievable with an exponential scaling of the ambient dimension
scaling, $p = O(\exp(cn))$ for some $0<c<1$, just as in parametric models.
The cost of nonparametric modeling through shape constraints is
reflected in the scaling with respect to the number of relevant
variables, which can scale as $s = o(n^{4/25})$.

@@

%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "paper-submit.tex" ***
%%% End: ***
